Lab2

### 2021-08-04 src/data/DataCleaning.Rmd
removed duplicate columns.

```{r clean density data}
density_f <- density %>%
  rename(
    county = County,
    total_pop = County.Population,
    density = X.Population.Density.Per.Sq.Mile
  ) %>%
  select(
    county, total_pop, density
  ) %>%
  mutate(
    total_pop = as.double(gsub('[,]', '', total_pop)),
    density = as.double(gsub('[,]', '', density))
  )

@@

#rm(d)
```

>>>>

```{r clean density data}
density_f <- density %>%
  rename(
    county = County,
    density = X.Population.Density.Per.Sq.Mile
    # total_pop = County.Population,
  ) %>%
  select(
    county, 
    density 
    #total_pop
  ) %>%
  mutate(
    #total_pop = as.double(gsub('[,]', '', total_pop)),
    density = as.double(gsub('[,]', '', density))
  )

@@

knitr::kable(head(d))
#rm(d)
```
